---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datardis 0.0.4

<!-- badges: start -->

<img src='https://cranlogs.r-pkg.org/badges/datardis'/><img src='https://cranlogs.r-pkg.org/badges/grand-total/datardis'/><img src='https://www.r-pkg.org/badges/version/datardis'/>

<!-- badges: end -->

The goal of datardis is to provide datasets from the **Doctor Who** and **Torchwood** TV shows.

Six datasets are available, three for each show:

ðŸŽžï¸ **Dr Who**

-   **drwho_episodes**

-   **drwho_directors**

-   **drwho_writers**

ðŸŽžï¸ **Torchwood**

-   **torchwood_episodes**

-   **torchwood_directors**

-   **torchwood_writers**

## Installation

You can download and install the package from CRAN:

```{r CRAN, echo=TRUE, eval=FALSE, warning=FALSE, message=FALSE}
install.packages("datardis")
```

You can install the development version from [GitHub](https://github.com/) with:

```{r dev version, echo=TRUE, eval=FALSE, warning=FALSE, message=FALSE}
devtools::install_github("KittJonathan/datardis")
```

## Examples

```{r examples, message=FALSE, warning=FALSE}

## Load packages
library(datardis)
library(tidyverse)

## Find maximum number of UK viewers for Doctor Who (in millions)
max(drwho_episodes$uk_viewers, na.rm = TRUE)

## Find who wrote the most episodes for Doctor Who
drwho_writers |>
     count(writer, sort = TRUE) |>
     head(5)

## Find who directed the most episodes for Doctor Who
drwho_directors |>
     count(director, sort = TRUE) |>
     head(5)

```
